---
title: "Rbasics-2 (Swaroop Srisailam)"
output:
  word_document: default
  html_notebook: default
---

# Vectors Arithmetic Operation

### Addition

```{r}
v <- c(3,9.5,6) 
t <- c(5, 8, 0)
print(v+t)
```

### Subtraction

```{r}
v <- c( 2,5.5,6) 
t <- c(8, 3, 4)
print(v-t)
```

### Multiplication

```{r}
v <- c( 2,5.5,6) 
t <- c(8, 3, 4)
print(v*t)
```

### Division

```{r}
v <- c( 2,5.5,6) 
t <- c(8, 3, 4)
print(v/t)
```

### Modulo

```{r}
a <- c( 2,5.5,6) 
b<- c(8, 3, 4)
print(a%%b)  
```

### **Quotient**

```{r}
a<- c(1,5,6)  
b<- c(8, 3, 4) 
print(a%/%b)
```

# **Colon Operator**

```{r}
s <- 0:9 
print(s)
```

# %in% Operator

```{r}
a <- 8 
b <- 18
t <- 1:10 
print(a %in% t) 
print(b %in% t)

```

# **%\*% Operator**

```{r}
M = matrix( c(1,1,0,0), nrow=2,ncol=2,byrow = TRUE) 
t = M %*% t(M) 
print(t)
```

# Control Structures

### If Else statement

```{r}
y <-8
  if(is.integer(y))
{ 
  print("y is an Integer") 
} else
 {
    print("y is not Integer")
 }
```

### While Loop

```{r}

i <- 1 

while (i <= 5) 
{  
  print(i) 
  i <- i + 1 
}

```

### **Repeat Loop**

```{r}
v <- c("Hola","Swaroop")
count <- 1
 repeat{ 
      print(v) 
      count <- count+1 
      if(count > 5)
      { break } 
    }

```

### For Loop

```{r}
v <- LETTERS[1:7]
 for ( i in v)
 { 
  print(i) 
 }

```

# Loop Control Statement

### Break

```{r}
v <- letters[1:7]
 for ( i in v)
 { 
   if(i == "c")
   {
     break
   }
  print(i) 
 }
# when loop reaches letter c , break will terminate the loop.
```

### Next

```{r}
v <- letters[1:7]
 for ( i in v)
 { 
   if(i == "c")
   {
     next
   }
  print(i) 
 }
# letter c is skipped.
```

# Data Analysis: Basics

### Importing Data

```{r}
data<- mtcars
head(data)
```

```{r}
summary(data)
```

### Average Weight of the cars

```{r}
mean(data$wt)
```

### Scatter plot between Mpg and Weight

```{r}
library(ggplot2)
ggplot(data, aes(x = wt, y = mpg)) +
    geom_point()


```

### Correlation between Weight and mpg

```{r}
x<-data$wt
y<-data$mpg
cor(x,y)
```

### Scatter plot between Mpg and Weight

### 
